Nope

### 2010-12-14 AffineLieAlgebras/MQFT2010/article.tex
More work on MQFT2010 paper

\begin{document}
\title{Nope}
\author{V D Lyakhovsky$^1$ and A A Nazarov$^2$}
%\address{$^{1,2}$ Theoretical Department, SPb State University,
%198904, Sankt-Petersburg, Russia }
%\eads{$^1$ \mailto{lyakh1507@nm.ru}, $^2$ \mailto{antonnaz@gmail.com}}

@@

\section{Introduction}
\label{sec:introduction}

We consider the reduction problem for simple Lie algebra modules. We study the reduction of Verma and irreducible finite-dimensional modules of the algebra to the modules of the subalgebra. We discuss the connection of the reduction with the Bernstein-Gelfand-Gelfand resolution. We show that different structures appear in the process of reduction, for example modules of contracted algebra and generalized Verma modules from parabolic category $\mathcal{O}^{\mathfrak{p}}$.

First of all, consider the following example. 
Let Lie algebra $\gf$ be $so(5)$ and subalgebra $\af\subset \gf$ be $so(3)$. There are different embeddings of $so(3)\to so(5)$. Here we limit ourselves to the regular ones. 
The root system of the algebra $so(5)$ consists of 8 roots. We denote simple roots by $\alpha_{1}=e_{1}-e_{2}$ and $\alpha_{2}=e_{2}$, where $e_{1},e_{2}$ form standard basis. The set of the positive roots is $\Delta^{+}=\left\{\alpha_{1}, \alpha_{1}+\alpha_{2}, \alpha_{1}+2\alpha_{2}, \alpha_{2}\right\}$. Each of these roots can be taken as the simple root of the subalgebra $so(3)$. At first we consider the subalgebra $so(3)$ with the root space spanned on $\beta=\alpha_{1}+2\alpha_{2}$. Verma module $M^{\mu}$ with the highest weight $\mu=\omega_{1}+2\omega_{2}=2\alpha_{1}+3\alpha_{2}$ is shown at Figure \ref{fig:B2_Verma}.
\begin{figure}[h!bt]
  \noindent\centering{
    \includegraphics[width=120mm]{B2_Verma}
  }
  \caption{Regular embedding of $A_1$ into $B_2$. Simple roots $\alpha_1, \alpha_2$ of $B_2$ are presented as the dashed vectors.
    The simple root $\beta = \alpha_1+2\alpha_2$ of $A_1$ is indicated as the grey vector. Dimensions of weight subspaces of Verma module $M^{(1,2)}$ are shown.}

@@

The branching coefficients are shown at Figure \ref{fig:B2_Verma_Branch2} for the different regular embeddings $so(3)\to so(5)$. Here we can see that the picture depends upon the embedding and looks similar to the Verma modules of some subalgebra.
\begin{figure}[h!bt]
  \noindent\centering{
    \includegraphics[width=120mm]{B2_Verma_Branch2}
  }
  \caption{Branching for the Verma modules}

@@

The formal character of Verma module is given by the expression
\begin{equation}
  \label{eq:17}
  \mathrm{ch} M^{\mu}=\frac{e^{\mu}}{\prod_{\alpha\in \Delta^{+}} \left(1-e^{-\alpha}\right)}
\end{equation}
The denominator $R=\prod_{\alpha\in \Delta^{+}} \left(1-e^{-\alpha}\right)$ can be rewritten as the sum over the Weyl group of the algebra
\begin{equation}
  \label{eq:20}
  R=\sum_{w\in W} \epsilon(w) e^{w\rho-\rho}.
\end{equation}
Since we consider the regular embeddings, all the positive roots of the subalgebra $\af$ are in the set of positive roots of the algebra $\gf$, $\Delta^{+}_{\af}\subset \Delta^{+}$. Then we can introduce $\tilde R$ and the carrier of its expansion $\Phi$:
\begin{equation}
  \label{eq:21}
  \tilde R=\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\af}} \left( 1 - e^{-\alpha}\right)=-\sum_{\gamma\in \Phi} s(\gamma) e^{-\gamma}
\end{equation}
The ordering of roots in $\Delta _{\af}$ induce the
natural ordering of the weights in $P_{\af}$. Denote by $\gamma _{0}$
the lowest vector of $\Phi _{\af\subset \frak{g}}$ . The set
\begin{equation}
\Gamma _{\af\rightarrow \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
\af\subset \frak{g}}\right\} \setminus \left\{ 0\right\}
\label{fan-defined}
\end{equation}
is called the \textit{injection fan}.

The root of the subalgebra is among the positive roots of the algebra. So  Verma module can be decomposed into the set of Verma modules of the subalgebra:
\begin{equation}
  \label{eq:18}
  \mathrm{ch}M^{\mu}=\sum_{\nu}b^{(\mu)}_{\nu} e^{\nu-\pi_{\af}\nu} \mathrm{ch}M^{\pi_{\af}\nu}_{\af}
\end{equation}
Using the equation \eqref{eq:21} we can write the recurrent relation for the branching coefficients $b^{(\mu)}_{\nu}$:
\begin{equation}
  \label{eq:19}
   b_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
        \delta_{\xi-\gamma_0,\mu}
        +\sum_{\gamma \in
          \Gamma _{\af \rightarrow \gf}}s\left( \gamma +\gamma _{0}\right) b_{\xi
          +\gamma }^{\left( \mu \right) }\right).
\end{equation}

@@

Consider finite-dimensional Lie algebra $\mathfrak{g}$  and its regular reductive subalgebra $\af\subset \mathfrak{g}$. Introduce the following objects.
\begin{definition}
  \label{def-1}
  Denote by $\Delta^{+}_{\afb}=\left\{\alpha\in \Delta^{+}_{\mathfrak{g}}:\forall \beta\in\Delta_{\af} \; \alpha\bot \beta\right\}$ the subset of the positive roots of $\mathfrak{g}$ orthogonal to the root system of $\af$.
\end{definition}

\begin{definition}
  \label{def-2}
  Denote by $W_{\afb}$ the subgroup of the Weyl group $W$ generated by the reflections $w_{\alpha}$ corresponding to the roots $\alpha\in \Delta^{+}_{\afb}$.
\end{definition}
\begin{mynote}
  The subgroup $W_{\afb}$ preserves $\Delta_{\af}$ since it is generated by the reflections in hyperplanes containing $\Delta_{\af}$.
\end{mynote}
\begin{definition}
  \label{def-3}
  The subsystem $\Delta_{\afb}=\Delta^{+}_{\afb}\cup \left(-\delta^{+}_{\afb}\right)$ determines the subalgebra $\af_{\bot}\subset \mathfrak{g}$.
\end{definition}
Let
\begin{equation*}
\frak{h}_{\perp }^{\ast }:=\left\{ \eta \in \frak{h}_{\perp \af}^{\ast
}|\forall \alpha \in \Delta _{\af}\cup \Delta _{\af_{\perp
}};\alpha \bot \eta \right\}
\end{equation*}
and consider the subalgebras
\begin{eqnarray*}
\widetilde{\af_{\perp }} &:&=\af_{\perp }\oplus \frak{h}_{\perp }
\\
\widetilde{\af} &:&=\af\oplus \frak{h}_{\perp }.
\end{eqnarray*}
Algebras $\af$ and $\af_{\perp }$ form the ''orthogonal pair''
$\left( \af,\af_{\perp}\right) $
of subalgebras in $\frak{g}$.

For the Cartan subalgebras we have the decomposition
\begin{equation}
\frak{h}=\frak{\frak{h}_{\af}}\oplus \frak{h}_{\af_{\perp }}\oplus
\frak{h}_{\perp }=\frak{\frak{h}_{\widetilde{\af}}}\oplus \frak{h}_{%
\af_{\perp }}=\frak{\frak{h}_{\widetilde{\af_{\perp }}}}\oplus
\frak{h}_{\af}.
\end{equation}
For the subalgebras of an orthogonal pair $\left( \af,\af_{\perp
}\right) $ we consider the corresponding Weyl vectors, $\rho _{\af}$
and $\rho _{\af_{\perp }}$ , and\ form the so called ''defects'' $%
\mathcal{D}_{\af}$ and $\mathcal{D}_{\af_{\perp }}$ of the
injection:
\begin{equation}
\mathcal{D}_{\af}:=\rho _{\af}-\pi _{\af}\rho ,
\end{equation}
\begin{equation}
\label{defect-perp}
\mathcal{D}_{\af_{\perp }}:=\rho _{\af_{\perp }}-\pi _{\af%
_{\perp }}\circ\rho .
\end{equation}
\begin{equation}
U:=\left\{ u\in W|\quad \mu _{\widetilde{\af_{\perp }}}\left( u\right)
\in \overline{C_{\widetilde{\af_{\perp }}}}\right\} \quad .
\label{U-def}
\end{equation}
For the same set $U$ introduce the weights
\begin{equation*}
\mu _{\af}\left( u\right) :=\pi _{\af}\circ\left[ u(\mu +\rho )-\rho %
\right] +\mathcal{D}_{\af_{\perp }}.
\end{equation*}
To simplify the form of relations we shall now on omit the sign "$\circ$" in projected
weights.

@@

\item Also we can generalize the whole construction to affine Lie algebras $\gf, \af$, since Weyl character formula and denominator identity have natural analogs in the theory of affine Lie algebras. The only subtle point is in the definition of projection $\pi$ to the subalgebra. The extension of the Killing form from the finite-dimensional simple Lie algebra $\co{\gf}$ to the affine Lie algebra $\gf$ is not positive-definite. For the imaginary root $\delta$ we have $(\delta,\delta)=0$. If we use this form for the projection to the root space of the affine subalgebra $\af$ we end up with $\delta\perp \beta; \beta\in \Delta_{\af}$ or $\pi_{\af}(n\delta)=0$. This is not what we want.

>>>>

\begin{document}
\title{Nope}
\author{V D Lyakhovsky$^1$ and A A Nazarov$^2$}

@@

\section{Introduction}

\label{sec:introduction}

The branching properties of Lie (affine Lie) algebras are highly important for
applications in quantum field theory. This concernes for example the
conformal field theory models \cite{difrancesco1997cft},\cite
{coquereaux2008conformal}.

% There are different approaches to deal with the branching coefficients. Some
% of them use the BGG resolution \cite{bernstein1975differential} (for
% Kac-Moody algebras the algorithm is described in \cite{kac1990idl},\cite
% {wakimoto2001idl}).

In this paper we demonstrate that for an arbitrary reductive subalgebra
branching is directly connected with the BGG resolution and in particular
exhibits the resolution properties in terms of the $\mathcal{O}^{p}$
category \cite{lepowsky1977generalization} (the parabolic generalization of the cathegory $%
\mathcal{O}$ \cite{bernstein1976category}).

To show this we use the recursive approach to branching presented in [our
preprint] (similar to the one used in \cite{ilyin812pbc} for maximal
embeddings). We consider the subalgebra $\frak{a}$ together with its
counterpart $\frak{a}_{\bot }$ ''orthogonal'' to $\frak{a}$ with respect to
the Killing form and also $\widetilde{\frak{a}_{\perp }}:=\frak{a}_{\perp
}\oplus \frak{h}_{\perp }$ where $\frak{h}=\frak{\frak{h}_{\frak{a}}}\oplus 
\frak{h}_{\frak{a}_{\perp }}\oplus \frak{h}_{\perp }$. For any reductive
algebra $\frak{a}$ the subalgebra $\frak{a}_{\bot }\hookrightarrow \frak{g}$
is regular and reductive. For a highest weight integrable module $L^{\left(
\mu \right) }$ and orthogonal pair of subalgebras $\left( \frak{a},\frak{a}%
_{\bot }\right) $ we consider the singular element $\Psi ^{\left( \mu
\right) }$ (the numerator in the Weyl character formula $ch\left( L^{\mu
}\right) =\frac{\Psi ^{\left( \mu \right) }}{\Psi ^{\left( 0\right) }}$, see
for example \cite{humphreys1997introduction}) the Weyl denominator $R=\Psi _{%
\frak{a}_{\bot }}^{\left( 0\right) }$ and the projection $\Psi _{\left( 
\frak{a},\frak{a}_{\bot }\right) }^{\left( \mu \right) }=\pi _{\frak{a}}%
\frac{\Psi _{\frak{g}}^{\left( \mu \right) }}{\Psi _{\frak{a}_{\bot
}}^{\left( 0\right) }}$. The element $\Psi _{\frak{g}}^{\left( \mu \right) }$
can be decomposed with respect to the set of Weyl numerators $\Psi _{\frak{a}%
_{\bot }}^{\left( \mu \right) }$ of $\frak{a}_{\bot }$. This decomposition
provides the possibility to construct the set of highest weight modules $L_{%
\widetilde{\frak{a}_{\perp }}}^{\mu _{\widetilde{\frak{a}_{\perp }}}}$. When
the injection \ $\frak{a}_{\bot }\hookrightarrow \frak{g}$ \ satisfies the
''standard parabolic'' conditions these modules give rise to the parabolic
Verma modules $M_{\left( \widetilde{\frak{a}_{\perp }}\hookrightarrow \frak{g%
}\right) }^{\mu _{\widetilde{\frak{a}_{\perp }}}}$ so that the initial
character $ch\left( L^{\mu }\right) $ is finally decomposed into the
alternating sum of such. On the other hand when the parabolic conditions are
violated the construction survives and exhibites a decomposition with
respect to a set of Verma modules $M_{\left( \widetilde{\frak{b}_{\perp }},%
\frak{g}\right) }^{\mu _{\widetilde{\frak{a}_{\perp }}}}$. In such a
situation the algebra $\widetilde{\frak{b}_{\perp }}$ is not a subalgebra in 
$\frak{g}$ but a contraction of $\widetilde{\frak{a}_{\perp }}$.

Some general properties of the proposed decompositions are formulated in
terms of a specific element $\Gamma _{\frak{a}\rightarrow \frak{g}}$ of the
group algebra $\mathcal{E}\left( \frak{g}\right) $ called ''the injection
fan''. Using this tool the simple and explicit algorithm for branching
coefficients computations applicable for an arbitrary (maximal or
nonmaximal) subalgebras of finite-dimensional or affine Lie algebras was
obtained in [our preprint].

Possible further developments are discussed in Section \ref{sec:conclusion}.

\subsection{Notation}

\label{sec:notation}

Consider affine Lie algebras $\frak{g}$ and $\frak{a}$ with the underlying
finite-dimensional subalgebras $\stackrel{\circ }{\frak{g}}$ and $\stackrel{%
\circ }{\frak{a}}$ and an injection $\frak{a}\hookrightarrow \frak{g}$ such
that $\frak{a}$ is a reductive subalgebra $\frak{a\subset g}$ with
correlated root spaces: $\frak{h}_{\frak{a}}^{\ast }\subset \frak{h}_{\frak{g%
}}^{\ast }$ and $\frak{h}_{\stackrel{\circ }{\frak{a}}}^{\ast }\subset \frak{%
h}_{\stackrel{\circ }{\frak{g}}}^{\ast }$\ . We use the following notations:

$L^{\mu }$\ $\left( L_{\frak{a}}^{\nu }\right) $\ --- the integrable module
of $\frak{g}$ with the highest weight $\mu $\ ; (resp. integrable $\frak{a}$
-module with the highest weight $\nu $ );

$r$ , $\left( r_{\frak{a}}\right) $ --- the rank of the algebra $\frak{g}$ $%
\left( \mathrm{{resp. }\frak{a}}\right) $ ;

$\Delta $ $\left( \Delta _{\frak{a}}\right) $--- the root system; $\Delta
^{+} $ $\left( \mathrm{{resp. }\Delta _{\frak{a}}^{+}}\right) $--- the
positive root system (of $\frak{g}$ and $\frak{a}$ respectively);

$\mathrm{mult}\left( \alpha \right) $ $\left( \mathrm{mult}_{\frak{a}}\left(
\alpha \right) \right) $ --- the multiplicity of the root $\alpha$ in $%
\Delta $ (resp. in $\left( \Delta _{\frak{a}}\right) $);

$\stackrel{\circ }{\Delta}$ , $\left( \stackrel{\circ }{\Delta _{\frak{a}}}%
\right)$ --- the finite root system of the subalgebra $\stackrel{\circ }{%
\frak{g}}$ (resp. $\stackrel{\circ }{\frak{a}}$);

$\mathcal{N}^{\mu }$ , $\left( \mathcal{N}_{\frak{a}}^{\nu }\right) $ ---
the weight diagram of $L^{\mu }$ $\left( \mathrm{{resp. }L_{\frak{a}}^{\nu }}%
\right) $ ;

$W$ , $\left( W_{\frak{a}}\right) $--- the corresponding Weyl group;

$C$ , $\left( C_{\frak{a}}\right) $--- the fundamental Weyl chamber;

$\bar{C}, \left(\bar{C_{\frak{a}}}\right)$ --- the closure of the
fundamental Weyl chamber;

$\rho $\ , $\left( \rho _{\frak{a}}\right) $\ --- the Weyl vector;

$\epsilon \left( w\right) :=\left( -1\right) ^{\mathrm{length}(w)}$;

$\alpha _{i}$ , $\left( \alpha _{\left( \frak{a}\right) j}\right) $ --- the $%
i $-th (resp. $j$-th) basic root for $\frak{g}$ $\left( \mathrm{{resp. }%
\frak{a}}\right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots ,r_{\frak{a}%
}\right) $;

$\delta $ --- the imaginary root of $\frak{g}$ (and of $\frak{a}$ if any);

$\alpha _{i}^{\vee }$ , $\left( \alpha _{\left( \frak{a}\right) j}^{\vee
}\right) $--- the basic coroot for $\frak{g}$ $\left( \mathrm{{resp. }\frak{a%
}}\right) $ , $i=0,\ldots ,r$ ;\ \ $\left( j=0,\ldots ,r_{\frak{a}}\right) $;

$\stackrel{\circ }{\xi }$ , $\stackrel{\circ }{\xi _{\left( \frak{a}\right) }%
}$ --- the finite (classical) part of the weight $\xi \in P$ , $\left( 
\mathrm{{resp. }\xi _{\left( \frak{a}\right) }\in P_{\frak{a}}}\right) $;

$\lambda =\left( \stackrel{\circ }{\lambda };k;n\right) $ --- the
decomposition of an affine weight indicating the finite part $\stackrel{%
\circ }{\lambda }$, level $k$ and grade $n$;

$P$ $\left( \mathrm{{resp.}P_{\frak{a}}}\right) $ \ --- the weight lattice;

$P^{+}$ $\left( \mathrm{{resp.}P_{\frak{a}}^{+}}\right) $ \ --- the dominant
weight lattice;

$m_{\xi }^{\left( \mu \right) }$ , $\left( m_{\xi }^{\left( \nu \right)
}\right) $ --- the multiplicity of the weight $\xi \in P$ \ $\left( \mathrm{{%
resp. }\in P_{\frak{a}}}\right) $ in the module $L^{\mu }$ , (resp. $\xi \in
L_{\frak{a}}^{\nu } $);

$ch\left( L^{\mu }\right) $ $\left( \mathrm{{resp. }ch\left( L_{\frak{a}%
}^{\nu }\right) }\right) $--- the formal character of $L^{\mu }$ $\left( 
\mathrm{{resp. }L_{\frak{a}}^{\nu }}\right) $;

$ch\left( L^{\mu }\right) =\frac{\sum_{w\in W}\epsilon (w)e^{w\circ (\mu
+\rho )-\rho }}{\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{%
\mathrm{{mult}\left( \alpha \right) }}}$ --- the Weyl-Kac formula;

$R:=\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{{%
mult}\left( \alpha \right) }}\quad $ $\left( \mathrm{resp.}R_{\frak{a}%
}:=\prod_{\alpha \in \Delta _{\frak{a}}^{+}}\left( 1-e^{-\alpha }\right) ^{%
\mathrm{mult}_{\frak{a}}\mathrm{\left( \alpha \right) }}\right) $--- the
Weyl denominator.

\section{Orthogonal subalgebra and the singular element}

\label{sec:recurr-form-branch}

Consider the highest weight $\mu \in P^{+}$ of an integrable module $L^{\mu
} $ of $\frak{g}$ and let $\frak{a}\subset \frak{g}$ be a reductive
subalgebra of $\frak{g}$. Let $L^{\mu }$ be completely reducible with
respect to $\frak{a}$, 
\[
L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
}^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }. 
\]
Using the projection operator $\pi _{\frak{a}}$ (to the weight space $\frak{%
h_{a}}^{\ast }$) one can rewrite this decomposition in terms of formal
characters: 
\begin{equation}
\pi _{\frak{a}}ch\left( L^{\mu }\right) =\sum_{\nu \in P_{\frak{a}%
}^{+}}b_{\nu }^{(\mu )}ch\left( L_{\frak{a}}^{\nu }\right) .
\label{branching1}
\end{equation}
The module $L^{\mu }$ has the BGG-resolution (see [BGG] and [Humphrys]). All
the members of the filtration sequence are the direct sums of Verma modules
and all their highest weights $\nu $ are strongly linked to $\mu $: 
\[
\left\{ \nu \right\} =\left\{ w\left( \mu +\rho \right) -\rho |w\in
W\right\} . 
\]

\subsection{Orthogonal subalgebra}

Let us introduce the ''orthogonal partner'' $\frak{a}_{\bot }$ for a
reductive subalgebra $\frak{a}$ in $\frak{g}$.

Consider the root subspace $\frak{h}_{\perp \frak{a}}^{\ast }$ orthogonal to 
$\frak{a}$, 
\[
\frak{h}_{\perp \frak{a}}^{\ast }:=\left\{ \eta \in \frak{h}^{\ast }|\forall
h\in \frak{h}_{\frak{a}};\eta \left( h\right) =0\right\} , 
\]
and the roots (correspondingly -- positive roots) of $\frak{g}$ orthogonal
to $\frak{a}$, 
\begin{eqnarray*}
\Delta _{\frak{a}_{\perp }} &:&=\left\{ \beta \in \Delta _{\frak{g}}|\forall
h\in \frak{h}_{\frak{a}};\beta \left( h\right) =0\right\} , \\
\Delta _{\frak{a}_{\perp }}^{+} &:&=\left\{ \beta ^{+}\in \Delta _{\frak{g}%
}^{+}|\forall h\in \frak{h}_{\frak{a}};\beta ^{+}\left( h\right) =0\right\} .
\end{eqnarray*}
Let $W_{\frak{a}_{\perp }}$ be the subgroup of $W$ generated by the
reflections $w_{\beta }$ with the roots $\beta \in \Delta _{\frak{a}_{\perp
}}^{+}$ . The subsystem $\Delta _{\frak{a}_{\perp }}$ determines the
subalgebra $\frak{a}_{\perp }$ with the Cartan subalgebra $\frak{h}_{\frak{a}%
_{\perp }}$. Let 
\[
\frak{h}_{\perp }^{\ast }:=\left\{ \eta \in \frak{h}_{\perp \frak{a}}^{\ast
}|\forall h\in \frak{h}_{\frak{a}\oplus \frak{a}_{\perp }};\eta \left(
h\right) =0\right\} 
\]
so that $\frak{g}$ has the subalgebras 
\begin{eqnarray*}
\widetilde{\frak{a}_{\perp }} &:&=\frak{a}_{\perp }\oplus \frak{h}_{\perp }
\\
\widetilde{\frak{a}} &:&=\frak{a}\oplus \frak{h}_{\perp }.
\end{eqnarray*}
Algebras $\frak{a}$ and $\frak{a}_{\perp }$ form the ''orthogonal pair'' $%
\left( \frak{a},\frak{a}_{\perp }\right) $ of subalgebras in $\frak{g}$.

For the Cartan subalgebras we have the decomposition 
\begin{equation}
\frak{h}=\frak{\frak{h}_{\frak{a}}}\oplus \frak{h}_{\frak{a}_{\perp }}\oplus 
\frak{h}_{\perp }=\frak{\frak{h}_{\widetilde{\frak{a}}}}\oplus \frak{h}_{%
\frak{a}_{\perp }}=\frak{\frak{h}_{\widetilde{\frak{a}_{\perp }}}}\oplus 
\frak{h}_{\frak{a}}.
\end{equation}
For the subalgebras of an orthogonal pair $\left( \frak{a},\frak{a}_{\perp
}\right) $ we consider the corresponding Weyl vectors, $\rho _{\frak{a}}$
and $\rho _{\frak{a}_{\perp }}$ , and\ form the so called ''defects'' $%
\mathcal{D}_{\frak{a}}$ and $\mathcal{D}_{\frak{a}_{\perp }}$ of the
injection: 
\begin{equation}
\mathcal{D}_{\frak{a}}:=\rho _{\frak{a}}-\pi _{\frak{a}}\rho ,
\end{equation}
\begin{equation}
\mathcal{D}_{\frak{a}_{\perp }}:=\rho _{\frak{a}_{\perp }}-\pi _{\frak{a}%
_{\perp }}\rho .
\end{equation}

For the highest weight $\mu \in P^{+}$ consider the linked weights $\left\{
\left( w(\mu +\rho )-\rho \right) |w\in W\right\} $ and their projections to 
$h_{\widetilde{\frak{a}_{\perp }}}^{\ast }$ additionally shifted by the
defect $-\mathcal{D}_{\frak{a}_{\perp }}$: 
\[
\mu _{\widetilde{\frak{a}_{\perp }}}\left( w\right) :=\pi _{\widetilde{\frak{%
a}_{\perp }}}\left[ w(\mu +\rho )-\rho \right] -\mathcal{D}_{\frak{a}_{\perp
}},\quad w\in W. 
\]
In the case we do consider here among the weights $\left\{ \mu _{\widetilde{%
\frak{a}_{\perp }}}\left( w\right) |w\in W\right\} $ one can always choose
those located in the fundamental chamber $\overline{C_{\widetilde{\frak{a}%
_{\perp }}}}$. Let $U$ be the set of representatives $u$ for the classes $%
W/W_{\frak{a}_{\perp }}$ such that

\begin{equation}
U:=\left\{ u\in W|\quad \mu _{\widetilde{\frak{a}_{\perp }}}\left( u\right)
\in \overline{C_{\widetilde{\frak{a}_{\perp }}}}\right\} \quad .
\label{U-def}
\end{equation}
For such a set $U$ introduce the weights 
\[
\mu _{\frak{a}}\left( u\right) :=\pi _{\frak{a}}\left[ u(\mu +\rho )-\rho %
\right] +\mathcal{D}_{\frak{a}_{\perp }}. 
\]

Note that the subalgebra $\afb$ is regular by definition since it is built on the roots of the
algebra $\gf$.

Consider the Weyl-Kac formula for $ch\left( L^{\mu }\right) $ in terms of
singular elements \cite{humphreys1997introduction}: 
\begin{equation}
ch\left( L^{\mu }\right) =\frac{\Psi ^{\left( \mu \right) }}{\Psi ^{\left(
0\right) }}=\frac{\Psi ^{\left( \mu \right) }}{R},  \label{Weyl-Kac2}
\end{equation}
where 
\[
\Psi ^{\left( \mu \right) }:=\sum\limits_{w\in W}\epsilon (w)e^{w\circ (\mu
+\rho )-\rho }. 
\]
The same form will be used for the submodules $ch\left( L_{\frak{a}}^{\nu
}\right) $%
\[
ch\left( L_{\frak{a}}^{\nu }\right) =\frac{\Psi _{\frak{a}}^{\left( \nu
\right) }}{\Psi _{\frak{a}}^{\left( 0\right) }}=\frac{\Psi _{\frak{a}%
}^{\left( \nu \right) }}{R_{\frak{a}}}, 
\]
with 
\[
\Psi _{\frak{a}}^{\left( \nu \right) }:=\sum\limits_{w\in W_{\frak{a}%
}}\epsilon (w)e^{w\circ (\nu +\rho _{_{\frak{a}}})-\rho _{_{\frak{a}}}}. 
\]

Applying formula (\ref{Weyl-Kac2}) to the branching rule (\ref{branching1})
we get the relation connecting the singular elements $\Psi ^{\left( \mu
\right) }$ and $\Psi _{\frak{a}}^{\left( \nu \right) }$ : 
\begin{eqnarray}
\pi _{\frak{a}}\left( \frac{\sum_{w \in W}\epsilon (w )e^{w (\mu +\rho
)-\rho }}{\prod_{\alpha \in \Delta ^{+}}(1-e^{-\alpha })^{\mathrm{mult}%
(\alpha )}}\right) &=&\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{(\mu )}\frac{%
\sum_{w \in W_{\frak{a}}}\epsilon (w )e^{w (\nu +\rho _{\frak{a}})-\rho _{%
\frak{a}}}}{\prod_{\beta \in \Delta _{\frak{a}}^{+}}(1-e^{-\beta })^{\mathrm{%
mult}_{\frak{a}}(\beta )}},  \nonumber  \label{eq:4} \\
\pi _{\frak{a}}\left( \frac{\Psi ^{\left( \mu \right) }}{R}\right)
&=&\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{(\mu )}\frac{\Psi _{\frak{a}%
}^{\left( \nu \right) }}{R_{\frak{a}}}.
\end{eqnarray}
Here $\Delta _{\frak{a}}^{+}$ is the set of positive roots of the subalgebra 
$\frak{a}$ (without loss of generality we consider them as vectors from the
positive root space $\frak{h}^{\ast +}$ of $\frak{g}$).

To describe the recurrent properties for branching coefficients $b_{\nu
}^{(\mu )}$ we shall use the technique first proposed in \cite{ilyin812pbc}.
One of the main tools is the set of weights $\Gamma _{\frak{a}\rightarrow 
\frak{g}}$ called the injection fan:

\begin{definition}
\label{fan-definition} For the product 
\begin{equation}
\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\bot }^{+}}\left( 1-e^{-\pi
_{\frak{a}}\alpha }\right) ^{\mathrm{mult}(\alpha )-\mathrm{mult}_{\frak{a}%
}(\pi _{\frak{a}}\alpha )}=-\sum_{\gamma \in P_{\frak{a}}}s(\gamma
)e^{-\gamma }  \label{eq:6}
\end{equation}
consider the carrier $\Phi _{\frak{a}\subset \frak{g}}\subset P_{\frak{a}}$
of the function $s(\gamma )=\det \left( \gamma \right) $ : 
\begin{equation}
\Phi _{\frak{a}\subset \frak{g}}=\left\{ \gamma \in P_{\frak{a}}|s(\gamma
)\neq 0\right\}   \label{eq:37}
\end{equation}
The ordering of roots in $\stackrel{\circ }{\Delta _{\frak{a}}}$ induce the
natural ordering of the weights in $P_{\frak{a}}$. Denote by $\gamma _{0}$
the lowest vector of $\Phi _{\frak{a}\subset \frak{g}}$ . The set 
\begin{equation}
\Gamma _{\frak{a}\rightarrow \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi
_{\frak{a}\subset \frak{g}}\right\} \setminus \left\{ 0\right\} 
\label{fan-defined}
\end{equation}
is called the \textit{injection fan}.
\end{definition}

It must be noticed that the injection fan is the universal instrument that
depend only on the injection.

\section{Branching for Verma modules}
\label{sec:branching-verma}

The formal character of Verma module is given by the expression
\begin{equation}
  \label{eq:17}
  \mathrm{ch} M^{\mu}=\frac{e^{\mu}}{\prod_{\alpha\in \Delta^{+}} \left(1-e^{-\alpha}\right)}
\end{equation}
The denominator $R=\prod_{\alpha\in \Delta^{+}} \left(1-e^{-\alpha}\right)$ can be rewritten as the sum over the Weyl group of the algebra
\begin{equation}
  \label{eq:20}
  R=\sum_{w\in W} \epsilon(w) e^{w\rho-\rho}.
\end{equation}
If we consider the regular embeddings, all the positive roots of the subalgebra $\af$ are in the set of positive roots of the algebra $\gf$, $\Delta^{+}_{\af}\subset \Delta^{+}$. Verma module can be decomposed into the set of Verma modules of the subalgebra:
\begin{equation}
  \label{eq:18}
  \mathrm{ch}M^{\mu}=\sum_{\nu}b^{(\mu)}_{\nu} e^{\nu-\pi_{\af}\nu} \mathrm{ch}M^{\pi_{\af}\nu}_{\af}
\end{equation}
Using the equation \eqref{eq:21} we can write the recurrent relation for the branching coefficients $b^{(\mu)}_{\nu}$:
\begin{equation}
  \label{eq:19}
   b_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
        \delta_{\xi-\gamma_0,\mu}
        +\sum_{\gamma \in
          \Gamma _{\af \rightarrow \gf}}s\left( \gamma +\gamma _{0}\right) b_{\xi
          +\gamma }^{\left( \mu \right) }\right).
\end{equation}

Inside the main Weyl chamber branching coefficients for Verma module coincide with the coefficients
for reduction of irreducible representations.

Now consider the following example. 
Let Lie algebra $\gf$ be $so(5)$ and subalgebra $\af\subset \gf$ be $so(3)$. There are different embeddings of $so(3)\to so(5)$. Here we limit ourselves to the regular ones. 
The root system of the algebra $so(5)$ consists of 8 roots. We denote simple roots by $\alpha_{1}=e_{1}-e_{2}$ and $\alpha_{2}=e_{2}$, where $e_{1},e_{2}$ form standard basis. The set of the positive roots is $\Delta^{+}=\left\{\alpha_{1}, \alpha_{1}+\alpha_{2}, \alpha_{1}+2\alpha_{2}, \alpha_{2}\right\}$. Each of these roots can be taken as the simple root of the subalgebra $so(3)$. At first we consider the subalgebra $so(3)$ with the root space spanned on $\beta=\alpha_{1}+2\alpha_{2}$. Verma module $M^{\mu}$ with the highest weight $\mu=\omega_{1}+2\omega_{2}=2\alpha_{1}+3\alpha_{2}$ is shown at Figure \ref{fig:B2_Verma}.
\begin{figure}[h!bt]
  \noindent\centering{
    \includegraphics[width=120mm]{B2_Verma.pdf}
  }
  \caption{Regular embedding of $A_1$ into $B_2$. Simple roots $\alpha_1, \alpha_2$ of $B_2$ are presented as the dashed vectors.
    The simple root $\beta = \alpha_1+2\alpha_2$ of $A_1$ is indicated as the grey vector. Dimensions of weight subspaces of Verma module $M^{(1,2)}$ are shown.}

@@

The branching coefficients are shown at Figure \ref{fig:B2_Verma_Branch2} for the different regular embeddings $so(3)\to so(5)$. Here we can see that the picture depends upon the embedding and looks similar to the Verma modules of some subalgebra.
\begin{figure}[h!bt]
  \noindent\centering{
    \includegraphics[width=120mm]{B2_Verma_Branch3}
  }
  \caption{Branching for the Verma modules}

@@

@@

@@

\end{enumerate}
